---
title: "Give Your Visualization Wings to Fly"
author: "Cameron Hansen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

# Introduction

Going over the data I was able to find the answers to some of the questions. In my first metric I decided to use a summary to describe the data. I looked at the average arrival delay for each one of the airports. According to the data it looks like Newark Liberty International Airport (EWR) comes in last. Next I filtered the data into just delta airlines to see which airport has the least amount of late arrivals. I created an late column, and then made the individual observation. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Which destination airport is the worst airport for arrival time? (you decide on the metric for "worst").



```{r include=FALSE}
library(tidyverse)
library(nycflights13)

new_flights <- drop_na(flights,origin,arr_delay) %>% 
  group_by(origin) %>% 
  mutate(avg_delay = mean(arr_delay)) %>% 
  ungroup()

```




```{r echo=FALSE}
ggplot(new_flights) +
  #geom_point(mapping = aes(x = arr_time, y = arr_delay, color = origin)) +
  stat_summary(mapping = aes(x = origin, y = arr_delay , group = origin, fill = origin), fun = "mean", geom = "bar") +
  labs(title = "Average Flight Delay", x = "Airport", y = "Delay Time (Minutes)")
```

If we look at the graph we can see that the Newark Liberty International Airport (EWR) has on average the longest delay in arrival time. 

## Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?


```{r echo = FALSE}
delta_flights <- filter(flights,carrier == "DL",na.rm = TRUE) %>% 
  mutate(late = ifelse(arr_delay > 0,TRUE,FALSE)) %>% 
  drop_na(arr_delay,origin)

```



```{r echo=FALSE}
ggplot(delta_flights) +
  geom_point(mapping = aes(x = origin,y = arr_delay/60, group = origin, color = late)) +
  geom_point(mapping = aes(x = origin,y = mean(arr_delay)/60, group = origin), color= "blue") +
  labs(title ="Delay in Delta Flights", x = "Airport", y = "Hours Late") +
  scale_color_manual(values = c("red","green"),breaks = c(TRUE,FALSE), labels = c("Late","On Time")) 
```

After seeing the graph it looks like for delta flights Newark Liberty International Airport (EWR) has the least amount of late flights. 
