---
title: "Exploratory Data Analysis"
author: "Cameron Hansen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Reading Notes

### EDA

#### Questions
 
- the right question with a near correct answer is better than the wrong question with a percise answer.
- What type of variation occurs within my variables
- What type of covariation occurs between my variables?

##### Variation
How much the  value changes from observation  to observation. You can find value in:
- Look for a pattern in the variation of the data.
- What calculations are most common and Why?
- Which values are rare? Why? Does that match your expectations?
- Can you see any unusual patterns? What might explain them?

You can group the data to find even more relations. 

##### Missing Values
Two solutions
- Remove Values
- Impute Vaules

##### CoVariation

A boxplot is a great way to see the covariance, the relationship between variables. 
- Reorder function
- Scattperplots

#### Patterns


## EDA Example

The code below is an example of the EDA process using the `starwars` data from the `tidyverse` package. (Make sure you have the `tidyverse` package installed!)

Run the code line-by-line and look at the output. Add a comment to each line of code that explains what it does/what insights it provides.

```{r}
library(tidyverse)
library(ggplot2)

dim(starwars)
colnames(starwars)

head(starwars)
glimpse(starwars)

?starwars

starwars %>% count(species)

mean(starwars$height)
mean(starwars$height, na.rm = TRUE)

summary(starwars$height)

cm_to_ft <- function(cm){
  ft = cm / 30.48
  return(ft)
}

starwars_2 <- starwars %>% mutate(height_ft = cm_to_ft(height)) 

dim(starwars_2)
colnames(starwars_2)

summary(starwars_2$height_ft)

ggplot(starwars_2, aes(height_ft)) + 
  geom_histogram()

starwars_2 %>% filter(height_ft == max(height_ft))
starwars_2 %>% filter(height_ft == max(height_ft, na.rm = TRUE))

# https://starwars.fandom.com/wiki/Yarael_Poof
```

## EDA Practice

Continue exploring the `starwars` data to gain additional insights, using [R4DS: Chapter 7](https://r4ds.had.co.nz/exploratory-data-analysis.html) as a guide.

It is ok if you don't understand the all code in Chapter 7. (That is what we'll be learning the next two weeks!) If writing your own code is a struggle, try the "copy, paste, and tweak" method.

```{r}
smaller <- diamonds %>% 
  filter(carat < 3)
  
ggplot(data = smaller, mapping = aes(x = carat)) +
  geom_histogram(binwidth = 0.1)
```

```{r}
glimpse(diamonds)
ggplot(data=diamonds)+
  geom_bar(mapping = aes(x=carat, y=))
```
